Man's not hot, Man can never be hot

### 2018-01-16 article/ms.tex

\section{Observations and Target Selection}
The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}. The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700$\AA$ to 9000$\AA$, and a nominal S/N ratio of 100. \citet{ho2017} cross-matches 9,952 stars between the low resolution spectra of LAMOST and the high resolution spectra from the APOGEE survey, and through a data driven spectral model. produces a 454,180 stellar data set. For this stellar data set the \textit{Cannon} predictive model infers $T_{eff}$, $log g$, $[Fe/H]$, and [$\alpha/M$] values.

The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. A negative residual as shown in (I know I shoould expand here on the psoter child)figure \ref{fig:figure1} illustrates an enhancement in Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. (thinking a sentence on why these lines are the strongest ?). The filter process had five requirements that each spectra for both enhancement lines had to meet to be considered a Barium star canidate, these included:

>>>>

\section{Observations and Target Selection}
The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}. The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700\AA\ to 9000\AA, and \todo{a nominal S/N ratio of 100 (is this true?)}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey.

The Barium stars analysed in this research were obtained by filtering for significant flux residuals, taken as, a disparity between the normalised LAMOST flux and the data driven model derived by \citet{ho2017}. A negative residual as shown in (I know I shoould expand here on the psoter child)figure \ref{fig:figure1} illustrates an enhancement in Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. \todo{These \ion{Ba}{II} and \ion{Sr}{II} resonance lines are very strong, allowing us to identify stars enhanced in neutron-capture elements given a well-fit model for the data}.
 (thinking a sentence on why these lines are the strongest ?). \todo{We used five filters that...} requirements that each spectra for both enhancement lines had to meet to be considered a Barium star candidate, these included:
